---
title: "Participant Dropout Report"
author: "Luran M."
date: "July 10, 2019"
output:
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes
    toc_float: yes
---
  
```{r setup, include=FALSE, warning = FALSE}
library(knitr, warn.conflicts = F, quietly = T)
library(tidyr, warn.conflicts = F, quietly = T)
library(dplyr, warn.conflicts = F, quietly = T)
library(ggplot2, warn.conflicts = F, quietly = T)
library(keyringr, warn.conflicts = F, quietly = T)
library(redcapAPI, warn.conflicts = F, quietly = T)
library(REDCapR, warn.conflicts = F, quietly = T)
library(lubridate, warn.conflicts = F, quietly = T)
#Create path to and api link to RedCaps
credential_label <- "beach_api"
credential_path <- paste(Sys.getenv("USERPROFILE"), '\\DPAPI\\passwords\\', Sys.info()["nodename"], '\\', credential_label, '.txt', sep="")
uri <- "https://redcap.ctsi.ufl.edu/redcap/api/"
beach_token<-decrypt_dpapi_pw(credential_path)
```

```{r variable selection, include=FALSE}
# Create connections
rcon <- redcapConnection(url=uri, token=beach_token)
# variables
desired_fields=c("test_id","redcap_event_name",
                 "beach_part_drop_out",
                 "beach_drop_reason",
                 "beach_last_visit",
                 "beachphone_mod",
                 "mom2wk_mod",
                 "mom3t_prepreg_bmi",
                 "mom3t_delivery_location")
# dropped participants
dropped.records.v1=c("BLS006A",
                     "BLS010A",
                     "BLS015A",
                     "BLS026A",
                     "BLS029A",
                     "BLS037A",
                     "BLS039A",
                     "BLS050A",
                     "BLS054A")
# pull data
ds <- data.frame(desired_fields)
dat<- redcap_read(
  batch_size=300,
  records= dropped.records.v1,
  redcap_uri = uri, 
  token      = beach_token, 
  fields     = desired_fields
  )$data
head(dat)
# reformat data
#--------------
# note: you will need to look in redcap data dictionary for values to recode
dat.f=dat %>%
  select(-redcap_event_name,-redcap_repeat_instrument,-redcap_repeat_instance) %>%
  mutate(beach_part_drop_out = recode(beach_part_drop_out, "1"="dropped","2"="not-dropped"),
         beach_last_visit    = recode(beach_last_visit, "1"="3rd_tri","2"="2wks","3"="2mon","4"="6mon","5"="12mon"),
         beachphone_mod = recode(beachphone_mod, "1"="vaginally","2"="c-section"),
         mom2wk_mod    = recode(mom2wk_mod, "1"="vaginally","2"="c-section"),
         delivery_locations = recode(mom3t_delivery_location, "1"= "UF Shands","2"="North Florida Regional","3"="other", "4"="I don't know","NA"="dropped participant didn't provide location"))%>%
  #group_by(test_id) %>%
  #arrange(mom3t_prepreg_bmi) %>%
  #mutate(prepreg_bmi= dplyr::first(mom3t_prepreg_bmi)) %>%
  #arrange(beach_last_visit) %>%
  #mutate(beach_last_visit2= dplyr::first(beach_last_visit)) %>%
  #arrange(test_id) %>%
  #select(-beach_last_visit, -mom3t_prepreg_bmi) %>%
#select(test_id, prepreg_bmi, beach_last_visit2) %>%
  distinct()
```

# Study Visit
```{r echo=FALSE}
bar_chart=dat.f %>% 
  group_by(beach_last_visit) %>% 
  tally()
# sort study visits by making variable a factor
bar_chart$beach_last_visit <- factor(bar_chart$beach_last_visit,levels = c("3rd_tri", "2wks", "2mon"))
# plot, add counts to figure
p=ggplot(data=bar_chart, aes(x=beach_last_visit, y=n)) + geom_bar(colour="black", stat="identity") + geom_text(aes(label=n), vjust=-0.4) 
p + ggtitle("Dropped participants last study visit") +
  xlab("study visit") + ylab("counts")
```

##Mode of delivery for participant:
# ```{r echo=FALSE}
# test<-dat%>%
#   select(test_id,beach_part_drop_out)%>%
#   filter(beach_part_drop_out==1)%>%
#   distinct(test_id)
`
##Delivery Location of dropped participants:``
```{r echo=FALSE}
bar_chart=dat.f %>% 
  select(delivery_locations,test_id,beach_last_visit)%>%
  group_by(delivery_locations, test_id, beach_last_visit) %>% 
  summarize(count=n())

g <- ggplot(bar_chart, aes(delivery_locations, count))
g+ geom_bar(stat="identity", width =0.5, fill="tomato2")+
  labs(title="dropped partcipant delivery location")

#delivery_locations[is.na(delivery_locations)]<-"dropped participant didn't provide location"

## sort study visits by making variable a factor
#
#
#
## plot, add counts to figure
#p=ggplot(bar_chart, aes(x=beach_last_visit2, y=count, #mom3t_delivery_location))+ scale_fill_brewer(palette = "spectral")
#p + geom_histogram(aes(fill=factor(mom3t_delivery_location)), #stat="identity",
#                 bin=24,
#                 col="black",
#                 size=.1)
#                






```
##Pre-pregnant BMI of dropped participants:
```{r echo=FALSE}
  newDat <- dat.f %>%
  group_by(test_id) %>%
  arrange(mom3t_prepreg_bmi) %>%
  mutate(prepreg_bmi= dplyr::first(mom3t_prepreg_bmi)) %>%
  arrange(beach_last_visit) %>%
  mutate(beach_last_visit2= dplyr::first(beach_last_visit)) %>%
  arrange(test_id) %>%
  select(-beach_last_visit, -mom3t_prepreg_bmi) %>%
  select(test_id, prepreg_bmi, beach_last_visit2) %>%
  distinct()

ggplot(data=newDat, aes(x=test_id, y=prepreg_bmi, group=beach_last_visit2)) +
  geom_line()+
  geom_point()
# Change line types
ggplot(data=newDat, aes(x=test_id, y=prepreg_bmi, group=beach_last_visit2)) +
  geom_line(linetype="dashed", color="blue", size=1.2)+
  geom_point(color="red", size=3)
```




###If empty, then dropped participant didn't provide location
